Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-06 paper/paper.tex
minor fix
pass on text

%% Our infrastructure reported a total of \nofuzzAll{} buckets, including
%% \lo{} and \hi{}, that resulted in \nofuzzBugs{} bug reports. Of the
%% total of \nofuzzAll{} buckets, we found that \nofuzzDuplicates\ were
%% duplicates and \nofuzzFalsePositives\ were false positives. Most of
%% the cases of duplicates were related to the Test262 conformance test
%% suite, which all \js{} should strive to pass but we found that it is
%% not uncommon for the engines to fail on some of these. For example,
%% \veight{} \nofuzzFalsePositives

We inspected each of those failures in detail according to the
following methodology. \Fix{..elaborate..}
Figure~\ref{tab:test-transplantation-bugs} shows
results. \Fix{...elaborate...}

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. A false positive is a bucket that did not lend
itself in a bug report. We identified five sources of imprecision. The
source ``not yet implemented'' indicates that the engine does not
implement some part of the specification. For example, at the time of
writing, Chakra does not implement various properties from the
\CodeIn{Symbol} object. The source ``invalid input'' indicates that
the test violated some part of the specification. For example, the
test indirectly invoked some function with unexpected
arguments\Fix{provide concrete example}. In all cases that we
analyzed, that happened because fuzzing produced an invalid test
input. The source ``timeout/ome''\footnote{ome is for out of memory
  error.} indicates that the test times out (we used a 3s time budget)
or runs out of memory. That happens because engines implement
different optimizations. For example, we found that only \jsc{}
implements tail-call optimization to avoid tail
recursion. Consequently, for a certain input, \jsc{} finishes
execution quickly whereas other engines time out. The source
``implementation-dependent'' is as defined in
Section~\ref{sec:imp-dep-behavior}.\Fix{provide concrete example} The
source ``future feature'' corresponds to the case where a feature will
be part of the spec but some engines already implemented it, making a
test that uses the feature to pass only in those engines.

\begin{table}[t]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    %% not yet implemented & 8 & - & - \\
    %% invalid input & 0 & - & - \\
    %% timeout/ome & 13 & - & - \\
    %% implementation-dependent & 3 & - & - \\
    %% future feature & 3 & - & - \\
    not yet implemented & - & - \\
    invalid input & - & - \\
    timeout/ome & - & - \\
    implementation-dependent & - & - \\
    future feature & - & - \\
    \bottomrule     
  \end{tabular}
\end{table}

>>>>

The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
false and true positives observed with test transplantation. The top
piechart shows false alarms.  It is important to stress that all the
``transplanted'' tests should have passed in these cases. The absolute
number of tests is shown in parentheses to the right side of the
explanation for the false positive. The sources of false alarm are as
follows:

\begin{itemize}
  \item \textbf{Undefined.} Implementation-dependent behavior as per
    ECMA262 specification~\cite{ecmas262-spec}. For example, \Fix{XXX}
  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} Because target engine does not optimize code as the
    original engine did, test fails to finish at the time limit
    specified in the test or runs out of memory. For example, we found
    that only \jsc{} implements tail-call optimization to avoid tail
    recursion.
  \item \textbf{Not implemented.} Test fails because it covers
    function in the spec which is yet to be implemented. For example,
    at the time of writing, Chakra did not implement various
    properties from the \mcodeid{Symbol} object. A test that refers to
    this object will fail in \chakra{}.
  \item \textbf{Future Feature.} Test fails because it uses a feature
    that is available in the original engine, but still not standard,
    and the target engine does not support that feature. For example,
    \Fix{XXX}
  \item \textbf{Error message mismatch.} Test fails because it
    compares an error message, which is not portable across
    engines. For example, \Fix{a test from the engine XXX compares the
      string encapsulated in the object of type YYY. The engine ZZZ
      fails because it produces the string AAA while expecting the
      string BBB.}
\end{itemize}

In summary, we observed that \Fix{...elaborate...}

Considering true positives, \Fix{...elaborate...}

\begin{figure}[h]
  \centering
  \subfloat[\label{fig:falsepositives}False Positives]{%
    \includegraphics[trim=0 150 0 100,clip,width=0.4\textwidth]{R/piecharts/falsepositives}
  }
  \label{1a}\hfill
  \subfloat[\label{fig:truepositives}True Positives]{%
    \includegraphics[trim=0 150 0 150,clip,width=0.4\textwidth]{R/piecharts/truepositives}    
  }
  \label{1b}\\
  \caption{\label{fig:piecharts-transplantation}False and True positives.}
\end{figure}

Figure~\ref{tab:test-transplantation-bugs} shows
results. \Fix{...elaborate...}

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. A false positive is a bucket that did not lend
itself in a bug report. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of one, which
emerges with fuzzing. The source ``invalid input'' indicates that the
test violated some part of the specification. For example, the test
indirectly invoked some function with unexpected arguments\Fix{provide
  concrete example}.

\begin{table}[t]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    Undefined & - & - \\
    Timeout/OME & - & - \\
    Not Implemented & - & - \\
    Future Feature & - & - \\
    Error Message Mismatch & - & - \\    
    Invalid Input & - & - \\    
    \bottomrule     
  \end{tabular}
\end{table}
